### 2020-04-01 SIAM_TEMPLATE/PaperSDE.tex
Fix

\documentclass[10pt]{article}

@@

\begin{document}
\maketitle

\textbf{Abstract.} We study the problem of drift estimation for two-scale continuous time series. We set ourselves in the framework of overdamped Langevin equations, for which a single-scale surrogate homogenized equation exists. In this setting, estimating the drift coefficient of the homogenized equation requires pre-processing of the data, often in the form of subsampling. We avoid subsampling by filtering the data with an appropriate kernel function and compute maximum likelihood estimators based on the filtered process. We show that the estimators we propose are asymptotically unbiased and demonstrate numerically the advantages of our method with respect to subsampling. Finally, we show how our filtering methodology can be combined with Bayesian techniques and provide a full uncertainty quantification of the inference procedure.

\textbf{AMS subject classifications.} 62F15, 65C30, 62M05, 74Q10.

\textbf{Keywords.} Parameter inference, diffusion process, data-driven homogenization, filtering, Bayesian inference, Langevin equation.

@@

\subsubsection{The influence of $\beta$}\label{sec:Num_Param3}
We finally test the variability of the estimator with respect to $\beta$ in \eqref{eq:filter}. We consider $\delta = \epl$, which corresponds to $\zeta = 1$ and seems to be the worst-case scenario for the filter, at least for $\beta = 1$. We consider again $\sigma = 0.5, 0.7, 1$ and vary $\beta = 1, 2, \ldots, 10$. Results, given in Figure \ref{fig:OUBeta}, show empirically that the estimator stabilizes fast with respect to $\beta$. Nevertheless, there is no theoretical guarantee supporting this empirical observation.

@@

\begin{proof}[Proof of Lemma \ref{lem:FPMarginal}] Integrating equation \eqref{eq:FPsystem} with respect to $z$ we obtain the stationary Fokker--Planck equation for the process $X^\epl$, i.e.
	\begin{equation}
	\label{FPx}
	\sigma (\phi^\epl)''(x) + \frac{\d}{\d x} \left( \left ( \alpha \cdot V'(x) + \frac{1}{\epl} p' \left ( \frac{x}\epl \right ) \right ) \phi^\epl(x)\right) = 0,
	\end{equation}
	whose solution is given by
	\begin{equation}
	\phi^\epl(x) = \frac{1}{C_{\phi^\epl}} \exp\left(- \frac{1}{\sigma} \alpha \cdot V(x) - \frac{1}{\sigma} p \left ( \frac{x}\epl \right )\right),
	\end{equation}
	and which proves \eqref{eq:marginalX}. In view of \eqref{eq:densityDecomposition} and \eqref{FPx}, equation \eqref{eq:FPsystem} can be rewritten as
	\begin{equation}\label{eq:psiEqualityPDE}
	\partial_x \left( \sigma \phi^\epl \psi^\epl \partial_x R^\epl \right) + \partial_z \left( \frac1\delta(z-x) \phi^\epl \psi^\epl R^\epl \right) = 0.
	\end{equation}
	We now multiply the equation above by a continuous differentiable function $f \colon \R^2 \to \R^N$, $f = f(x,z)$, and integrate with respect to $x$ and $z$. Then an integration by parts yields
	\begin{equation}
	\sigma \int_\R \int_\R \partial_x f(x,z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z = \frac1\delta \int_\R \int_\R \partial_z f(x,z) (x-z) \phi^\epl(x) \psi^\epl(z) R^\epl(x,z) \dd x \dd z,
	\end{equation}
	which implies the following identity in $\R^N$
	\begin{equation}
	\sigma \delta \int_\R \int_\R \partial_x f(x,z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z = \E^{\rho_\epl} \left[ \partial_z f(X^\epl,Z^\epl) (X^\epl-Z^\epl) \right].
	\end{equation}
	Finally, choosing 
	\begin{equation}
	f(x,z) = (x - z) V'(z) + V(z),
	\end{equation}
	we obtain the desired result.
\end{proof}

@@

	Let us introduce the notation 
	\begin{equation}
	\Delta(\epl) = \left| \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] - \Sigma \E^{\phi^0} [V''(X)] \right|,
	\end{equation}
	and note that the aim is to show that $\lim_{\epl \to 0} \Delta(\epl) = 0$. By the triangle inequality we get
	\begin{equation}
	\begin{aligned}
	\Delta(\epl) \le& \left| \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] - \sigma \E^{\eta^\epl} [V''(X^\epl) (1 + \Phi'(Y^\epl))^2] \right| \\
	&+ \left| \sigma \E^{\eta^\epl} [V''(X^\epl) (1 + \Phi'(Y^\epl))^2] - \Sigma \E^{\phi^0} [V''(X)] \right| \\
	\eqdef& \Delta_1(\epl) + \Delta_2(\epl).
	\end{aligned}
	\end{equation}
	We first study $\Delta_1(\epl)$ and due to the boundedness of $\Phi'$, Assumption \ref{as:regularityZeta} and Lemma \ref{cor:distanceZandX} we have
	\begin{equation}
	\Delta_1(\epl) \le C \E^{\eta^\epl} \abs{X^\epl - Z^\epl} \le C (\delta^{1/2} + \epl) = C (\epl^{\zeta/2} + \epl),
	\end{equation}
	which implies
	\begin{equation}
	\lim_{\epl \to 0} \Delta_1(\epl) = 0.
	\end{equation}
	We now consider $\Delta_2(\epl)$. Integrating equation \eqref{eq:FPSDEquadruple} with respect to $z$ and $b$ we obtain the Fokker-Planck equation for the stationary marginal distribution $\lambda \colon \R \times [0,L]$, $\lambda = \lambda(x,y)$, of the couple $(X^\epl,Y^\epl)$
	\begin{equation}
	\begin{aligned}
	\partial_x \left( \left( \alpha \cdot V'(x) + \frac1\epl p'(y) \right) \lambda \right) + \partial_y \left( \left( \frac1\epl \alpha \cdot V'(x) + \frac{1}{\epl^2} p'(y) \right) \lambda \right) & \\
	+ \sigma \left( \partial_{xx}^2 \lambda + \partial_{xy}^2 \left( \frac2\epl \lambda \right) + \partial_{yy}^2 \left( \frac{1}{\epl^2} \lambda \right) \right) &= 0,
	\end{aligned}
	\end{equation}
	whose solution is given by
	\begin{equation}
	\lambda(x,y) = \frac{1}{C_\lambda} \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right),
	\end{equation}
	where
	\begin{equation}
	\begin{aligned}
	C_{\lambda} &= \int_\R \int_0^L \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right) \dd x \dd y \\
	&= \left( \int_\R \exp \left( - \frac\alpha\sigma V(x) \right) \dd x \right) \left( \int_0^L \exp \left( - \frac1\sigma p(y) \right) \dd y \right) \\
	&\eqdef C_{\lambda_x} C_{\lambda_y}.
	\end{aligned}
	\end{equation}
	Therefore, since $\Sigma = K\sigma$ and by equations \eqref{eq:K_HOM} and \eqref{eq:phi0} we have
	\begin{equation}
	\begin{aligned}
	\sigma \E^{\eta^\epl} [V''(X^\epl) (1 + \Phi'(Y^\epl))^2] &= \sigma \int_\R \int_0^L V''(x) (1 + \Phi'(y))^2 \frac{1}{C_\lambda} \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right) \dd x \dd y \\
	&= \sigma \left( \int_\R V''(x) \frac{1}{C_{\lambda_x}} \exp \left( - \frac\alpha\sigma V(x) \right) \dd x \right) \\
	&\qquad \qquad \times \left( \int_0^L (1+\Phi'(y))^2 \frac{1}{C_{\lambda_y}} \exp \left( - \frac1\sigma p(y) \right) \dd y \right) \\
	&= \sigma K \E^{\phi^0}[V''(X)] = \Sigma \E^{\phi^0}[V''(X)],
	\end{aligned}
	\end{equation}
	which shows that $\Delta_2(\epl) = 0$ and completes the proof. \qed

@@

\bibliographystyle{siam}
\bibliography{anmc}
\end{document}

>>>>

\documentclass[review,onefignum,onetabnum]{siamonline190516}

@@

\begin{document}

\maketitle

\begin{abstract} We study the problem of drift estimation for two-scale continuous time series. We set ourselves in the framework of overdamped Langevin equations, for which a single-scale surrogate homogenized equation exists. In this setting, estimating the drift coefficient of the homogenized equation requires pre-processing of the data, often in the form of subsampling. We avoid subsampling by filtering the data with an appropriate kernel function and compute maximum likelihood estimators based on the filtered process. We show that the estimators we propose are asymptotically unbiased and demonstrate numerically the advantages of our method with respect to subsampling. Finally, we show how our filtering methodology can be combined with Bayesian techniques and provide a full uncertainty quantification of the inference procedure.
\end{abstract}

\begin{keywords} Parameter inference, diffusion process, data-driven homogenization, filtering, Bayesian inference, Langevin equation. 
\end{keywords}
\begin{AMS} 62F15, 65C30, 62M05, 74Q10. \end{AMS}

@@

\subsubsection{The second parameter of the filter}\label{sec:Num_Param3}
We finally test the variability of the estimator with respect to $\beta$ in \eqref{eq:filter}. We consider $\delta = \epl$, which corresponds to $\zeta = 1$ and seems to be the worst-case scenario for the filter, at least for $\beta = 1$. We consider again $\sigma = 0.5, 0.7, 1$ and vary $\beta = 1, 2, \ldots, 10$. Results, given in Figure \ref{fig:OUBeta}, show empirically that the estimator stabilizes fast with respect to $\beta$. Nevertheless, there is no theoretical guarantee supporting this empirical observation.

@@

\begin{proof}[Proof of Lemma \ref{lem:FPMarginal}] Integrating equation \eqref{eq:FPsystem} with respect to $z$ we obtain the stationary Fokker--Planck equation for the process $X^\epl$, i.e.
	\begin{equation}
	\label{FPx}
	\sigma (\phi^\epl)''(x) + \frac{\d}{\d x} \left( \left ( \alpha \cdot V'(x) + \frac{1}{\epl} p' \left ( \frac{x}\epl \right ) \right ) \phi^\epl(x)\right) = 0,
	\end{equation}
	whose solution is given by
	\begin{equation}
	\phi^\epl(x) = \frac{1}{C_{\phi^\epl}} \exp\left(- \frac{1}{\sigma} \alpha \cdot V(x) - \frac{1}{\sigma} p \left ( \frac{x}\epl \right )\right),
	\end{equation}
	and which proves \eqref{eq:marginalX}. In view of \eqref{eq:densityDecomposition} and \eqref{FPx}, equation \eqref{eq:FPsystem} can be rewritten as
	\begin{equation}\label{eq:psiEqualityPDE}
	\partial_x \left( \sigma \phi^\epl \psi^\epl \partial_x R^\epl \right) + \partial_z \left( \frac1\delta(z-x) \phi^\epl \psi^\epl R^\epl \right) = 0.
	\end{equation}
	We now multiply the equation above by a continuous differentiable function $f \colon \R^2 \to \R^N$, $f = f(x,z)$, and integrate with respect to $x$ and $z$. Then an integration by parts yields
	\begin{equation}
	\begin{aligned}
	\sigma \int_\R \int_\R \partial_x f(x,z) \phi^\epl(x) \psi^\epl(z) &\partial_x R^\epl(x,z) \dd x \dd z = \\
	&\frac1\delta \int_\R \int_\R \partial_z f(x,z) (x-z) \phi^\epl(x) \psi^\epl(z) R^\epl(x,z) \dd x \dd z,
	\end{aligned}
	\end{equation}
	which implies the following identity in $\R^N$
	\begin{equation}
	\sigma \delta \int_\R \int_\R \partial_x f(x,z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z = \E^{\rho_\epl} \left[ \partial_z f(X^\epl,Z^\epl) (X^\epl-Z^\epl) \right].
	\end{equation}
	Finally, choosing 
	\begin{equation}
	f(x,z) = (x - z) V'(z) + V(z),
	\end{equation}
	we obtain the desired result.
\end{proof}

@@

	Let us introduce the notation 
	\begin{equation}
	\Delta(\epl) = \left| \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] - \Sigma \E^{\phi^0} [V''(X)] \right|,
	\end{equation}
	and note that the aim is to show that $\lim_{\epl \to 0} \Delta(\epl) = 0$. By the triangle inequality we get
	\begin{equation}
	\begin{aligned}
	\Delta(\epl) \le& \left| \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] - \sigma \E^{\eta^\epl} [V''(X^\epl) (1 + \Phi'(Y^\epl))^2] \right| \\
	&+ \left| \sigma \E^{\eta^\epl} [V''(X^\epl) (1 + \Phi'(Y^\epl))^2] - \Sigma \E^{\phi^0} [V''(X)] \right| \\
	\eqdef& \Delta_1(\epl) + \Delta_2(\epl).
	\end{aligned}
	\end{equation}
	We first study $\Delta_1(\epl)$ and due to the boundedness of $\Phi'$, Assumption \ref{as:regularityZeta} and Lemma \ref{cor:distanceZandX} we have
	\begin{equation}
	\Delta_1(\epl) \le C \E^{\eta^\epl} \abs{X^\epl - Z^\epl} \le C (\delta^{1/2} + \epl) = C (\epl^{\zeta/2} + \epl),
	\end{equation}
	which implies
	\begin{equation}
	\lim_{\epl \to 0} \Delta_1(\epl) = 0.
	\end{equation}
	We now consider $\Delta_2(\epl)$. Integrating equation \eqref{eq:FPSDEquadruple} with respect to $z$ and $b$ we obtain the Fokker-Planck equation for the stationary marginal distribution $\lambda \colon \R \times [0,L]$, $\lambda = \lambda(x,y)$, of the couple $(X^\epl,Y^\epl)$
	\begin{equation}
	\begin{aligned}
	\partial_x \left( \left( \alpha \cdot V'(x) + \frac1\epl p'(y) \right) \lambda \right) + \partial_y \left( \left( \frac1\epl \alpha \cdot V'(x) + \frac{1}{\epl^2} p'(y) \right) \lambda \right) & \\
	+ \sigma \left( \partial_{xx}^2 \lambda + \partial_{xy}^2 \left( \frac2\epl \lambda \right) + \partial_{yy}^2 \left( \frac{1}{\epl^2} \lambda \right) \right) &= 0,
	\end{aligned}
	\end{equation}
	whose solution is given by
	\begin{equation}
	\lambda(x,y) = \frac{1}{C_\lambda} \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right),
	\end{equation}
	where
	\begin{equation}
	\begin{aligned}
	C_{\lambda} &= \int_\R \int_0^L \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right) \dd x \dd y \\
	&= \left( \int_\R \exp \left( - \frac\alpha\sigma V(x) \right) \dd x \right) \left( \int_0^L \exp \left( - \frac1\sigma p(y) \right) \dd y \right) \\
	&\eqdef C_{\lambda_x} C_{\lambda_y}.
	\end{aligned}
	\end{equation}
	Therefore, since $\Sigma = K\sigma$ and by equations \eqref{eq:K_HOM} and \eqref{eq:phi0} we have
	\begin{equation}
	\begin{aligned}
	\sigma \E^{\eta^\epl} [V''(X^\epl) (1 + \Phi'(Y^\epl))^2] &= \sigma \int_\R \int_0^L V''(x) 
	\begin{aligned}[t]
	&(1 + \Phi'(y))^2\\
	&\times \frac{1}{C_\lambda} \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right) \dd x \dd y 
	\end{aligned}
	\\
	&= \sigma \left( \int_\R V''(x) \frac{1}{C_{\lambda_x}} \exp \left( - \frac\alpha\sigma V(x) \right) \dd x \right) \\
	&\qquad \qquad \times \left( \int_0^L (1+\Phi'(y))^2 \frac{1}{C_{\lambda_y}} \exp \left( - \frac1\sigma p(y) \right) \dd y \right) \\
	&= \sigma K \E^{\phi^0}[V''(X)] = \Sigma \E^{\phi^0}[V''(X)],
	\end{aligned}
	\end{equation}
	which shows that $\Delta_2(\epl) = 0$ and completes the proof. \qed

@@

\bibliographystyle{siamplain}
\bibliography{anmc}
\end{document}
